---
title: "data mining project report"
---

```{r global_options, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```




```{r,echo=FALSE}
options( java.parameters = "-Xmx6g")

library(dplyr)
library(tidyr)

# Create example data frame

library(caret)

library('tidyverse')
library('tidymodels')
library('plotly')
library('skimr')
library(ggplot2)
library(mlr)
library(xgboost)
#pkgs <- c("factoextra",  "NbClust")
#install.packages(pkgs)
library('factoextra')
library('NbClust')
#install.packages('leaflet')
library('leaflet')
library('rgdal')
#install.packages('tigris')
library('tigris')
#install.packages('httr')
library('httr')
#install.packages('sp')
library('sp')
#install.packages('webshot')
library('webshot')

f = file.choose()
completeData<-read.csv(f)
completeData<-completeData %>% 
  filter(substr(completeData$X.randomControl.,1,3)==116)

#completeData<-completeData[,-c(1,39,250)]


colsToFactor <- c('bed_type','cancellation_policy','room_type','host_has_profile_pic','host_identity_verified','host_is_superhost','instant_bookable','is_location_exact','require_guest_phone_verification','require_guest_profile_picture','requires_license','review_scores_accuracy','review_scores_checkin','review_scores_cleanliness','review_scores_communication','review_scores_location','review_scores_value')
completeData <- completeData %>%
  mutate_at(colsToFactor, ~factor(.))


#completeData$high_booking_rate<-as.factor(completeData$high_booking_rate)
#colnames(completeData)

colsToFactor<-c(43:245)
completeData <- completeData %>%
  mutate_at(colsToFactor, ~factor(.))
#completeData<-completeData[,-96]



gc()



#completeData$high_booking_rate<-as.factor(completeData$high_booking_rate)
#levels(completeData$high_booking_rate) <- c("No", "Yes")


gc()

#completeData<-completeData %>% filter(market=='New York')

set.seed(1234)

library(data.table)

library(Matrix)



myvars <- c("high_booking_rate", "host_is_superhost","amenities_.Self.check.in.","host_response_time",
            "amenities_.Hot.water.","amenities_.Free.street.parking.","amenities_.Dishes.and.silverware.","amenities_Refrigerator","amenities_.Coffee.maker.","host_listings_count","amenities_Microwave","cancellation_policy","availability_90","availability_60","availability_30","availability_365","amenities_.Extra.pillows.and.blankets.","longitude","amenities_.Cooking.basics.","amenities_.Luggage.dropoff.allowed.","latitude","amenities_.Bed.linens.","amenities_.Hair.dryer.","amenities_Keypad","minimum_nights","extra_people","cleaning_fee","amenities_.Family.kid.friendly.","guests_included","price","property_type","amenities_Shampoo","amenities_Stove","amenities_Iron","amenities_.translation.missing..en.hosting_amenity_50.","review_scores_value","amenities_.Long.term.stays.allowed.","price_score","amenities_.24.hour.check.in.","host_response_rate","amenities_Hangers","amenities_.Garden.or.backyard.","amenities_Oven","amenities_.Fire.extinguisher.","amenities_Gym","amenities_.Laptop.friendly.workspace.","amenities_Elevator","maximum_nights","amenities_.Patio.or.balcony.","review_scores_accuracy","review_scores_checkin","amenities_Lockbox","host_verifications","amenities_.First.aid.kit.","amenities_.Carbon.monoxide.detector.","security_deposit","amenities_Internet","review_scores_communication","amenities_.Single.level.home.","amenities_Pool","amenities_Essentials","amenities_.Pets.live.on.this.property.","amenities_.Bedroom.comforts.","amenities_.Bathroom.essentials.","amenities_.Toilet.paper.","amenities_.Well.lit.path.to.entrance.","amenities_Dog.s.","amenities_.Bath.towel.","amenities_.Smoke.detector.","bathrooms","accommodates","review_scores_location","amenities_Wifi","review_scores_value","review_scores_cleanliness","host_identity_verified","is_location_exact","requires_license","require_guest_profile_picture","amenities","host_sinceD","amenities_.Pack..n.Play.travel.crib.","amenities_.No.stairs.or.steps.to.enter.","amenities_.Body.soap.","amenities_.Room.darkening.shades.","amenities_.Safety.card.","amenities_Bathtub","amenities_.Children.s.books.and.toys.","amenities_Heating","amenities_.Hot.tub.","amenities_.Wide.entrance.for.guests.","amenities_Dishwasher","amenities_.Extra.space.around.bed.","amenities_Cat.s.","amenities_Netflix","amenities_.Cable.TV.","amenities_.Luggage.dropoff.allowed.","amenities_.Smart.TV.","market","amenities_Internet","bedrooms","amenities_Printer","amenities_.Disabled.parking.spot.","amenities_.Mini.fridge.","amenities_.Gas.oven.","amenities_.24.hour.check.in.","amenities_.Full.kitchen.","amenities_Washer","amenities_Other","instant_bookable","amenities_.Formal.dining.area.","room_type","review_scores_ratingOG")

completeData <- completeData[myvars]

library(dummies)

completeData2 <- dummy.data.frame(completeData, sep = ".")

#levels(completeData$host_is_superhost) <- c(0,1,2)
#target<-completeData2$high_booking_rate

dffTrain <- completeData2%>% sample_frac(0.7)
target<-dffTrain$high_booking_rate
dffTest <- dplyr::setdiff(completeData2, dffTrain) 

trainMatrix <- data.matrix(dffTrain[-1])
testMatrix <- data.matrix(dffTest[-1])
trainMatrix<-scale(trainMatrix)
testMatrix<-scale(testMatrix)

#dim(dffTrain)

param <- list("objective" = "binary:logistic",scoring='auc')


nround = 195            #this number is the number of trees when test mlogloss is minimum during cross-validation
bst = xgboost(data = trainMatrix, label = target, param=param, nrounds = nround)

#predict the model

ypred = predict(bst, testMatrix)

pred <-  as.numeric(ypred > 0.30)
CM_Validation <- confusionMatrix(as.factor(pred),as.factor(dffTest$high_booking_rate))
CM_Validation


importance <- xgb.importance(feature_names = colnames(completeData2[-1]), model = bst)
importance



```

```{r}
importance

CM_Validation
```


We have used Xgboost as our model for predicting booking rate for the market of new york. Model has accuracy of 87.93 for the threshold that we have kept as 0.25 with high sensitivity of 0.8918 and specificity of 0.8321. Since our first business proposal is for investors looking for new acquisition of property we want to present them with as many correct options as possible.Thus we have kept the threshold of our model at 0.25 in order to increase the specificity and maintain trade off between accuracy, specificity and sensitivity. Even though this impacts the sensitivity and accuracy by a small margin it is not significant and for our business proposal this threshold is more appropriate.

### New properties added in New York over time


airbnbTrain.csv

```{r}
f1 = file.choose()
Data <- read_csv(f1)
```


```{r,echo=FALSE}
library("dplyr")

NyData1 <- Data %>% 
  filter(substr(Data$`{randomControl}`, 1,3) == 116)

```

```{r,echo=FALSE}
NyData1$host_since = as.Date(NyData1$host_since, "%m/%d/%Y")
NyData1$host_since = as.factor(format(NyData1$host_since, "%Y"))
```

```{r,echo=FALSE}
plot1 <- ggplot(data = NyData1) + 
  geom_histogram(aes(host_since), stat = "count", fill = 'red',alpha = 0.85) + 
  theme_minimal(base_size=13)+xlab("")+ylab("") + 
  ggtitle("The Number of New Property in New York")

plot1
```





```{r,echo=FALSE}
f2 = file.choose()
completeData<-read.csv(f2)

completeData<-completeData %>% filter(substr(completeData$X.randomControl., 1,3) == 116)

f3 = file.choose()
ny_zipcodes_geom <- readOGR(f3, verbose = F)

completeData_visual <- completeData
completeData_visual_spdf <- completeData_visual
coordinates(completeData_visual_spdf) <- ~longitude + latitude
proj4string(completeData_visual_spdf) <- proj4string(ny_zipcodes_geom)
matches <- over(completeData_visual_spdf, ny_zipcodes_geom)
completeData_visual <- cbind(completeData_visual, matches)
completeData_visual <- completeData_visual %>% mutate(zcta = fct_explicit_na(zcta))

completeData_visual_summary <- completeData_visual %>% group_by(zcta) %>% summarise(avg_booking_rate = mean(high_booking_rate), avg_location_score = mean(review_scores_location), avg_price = mean(price))

map_data <- geo_join(ny_zipcodes_geom, completeData_visual_summary, "zcta", "zcta")

popup_location <- paste0("Zipcode: ", as.character(map_data$zcta), " Location_Score: ", as.character(map_data$avg_location_score))
popup_booking <- paste0("Zipcode: ", as.character(map_data$zcta), " Booking_Rate: ", as.character(map_data$avg_booking_rate))
popup_price <- paste0("Zipcode: ", as.character(map_data$zcta), " Price: ", as.character(map_data$avg_price))
pal_location <- colorNumeric (palette = c("red", "green", "blue"), domain = map_data$avg_location_score)
pal_booking <- colorNumeric (palette = c("red", "green", "blue"), domain = map_data$avg_booking_rate)
pal_price <- colorNumeric (palette = c("yellow", "green", "blue"), domain = map_data$avg_price)

```



```{r,echo=FALSE}
leaflet(map_data) %>%
addTiles() %>%
addPolygons(fillColor = ~pal_location(avg_location_score), fillOpacity = 0.7, weight = 0.7, color = "#b2aeae", popup = popup_location) %>% addProviderTiles("CartoDB.Positron") %>% setView(-73.98, 40.75, zoom = 11) %>% addLegend(pal = pal_location, values = map_data$avg_location_score, position = "bottomright", title = "Average Location Score")
```



```{r,echo=FALSE}

leaflet(map_data) %>%
addTiles() %>%
addPolygons(fillColor = ~pal_booking(avg_booking_rate), fillOpacity = 0.7, weight = 0.7, color = "#b2aeae", popup = popup_booking) %>% addProviderTiles("CartoDB.Positron") %>% setView(-73.98, 40.75, zoom = 11) %>% addLegend(pal = pal_booking, values = map_data$avg_booking_rate, position = "bottomright", title = "Average Booking Rate")

```



```{r,echo=FALSE}
leaflet(map_data) %>%
addTiles() %>%
addPolygons(fillColor = ~pal_price(avg_price), fillOpacity = 0.7, weight = 0.7, color = "#b2aeae", popup = popup_price) %>% addProviderTiles("CartoDB.Positron") %>% setView(-73.98, 40.75, zoom = 11) %>% addLegend(pal = pal_price, values = map_data$avg_price, position = "bottomright", title = "Average Price")
```



```{r,echo=FALSE}
f5 = file.choose()
dataPlot <- read_csv(f5)
dataplot<-na.omit(dataPlot,cols='host_is_superhost')
dataNySuperHost <- dataPlot %>% 
  select(host_is_superhost, host_response_rate, review_scores_rating)
plot9 <- dataNySuperHost %>% 
  ggplot(aes(x = host_response_rate, y = review_scores_rating, color = host_is_superhost)) + geom_point()

plot9+  theme(
  axis.text.x = element_blank())


```



```{r,echo=FALSE}
f4 = file.choose()
completeData<-read.csv(f4)
completeData<-completeData %>% 
  filter(substr(completeData$X.randomControl.,1,3)==116)

#colnames(completeData)
#completeData<-completeData[,-c(1,39,250)]


colsToFactor <- c('bed_type','cancellation_policy','room_type','host_has_profile_pic','host_identity_verified','host_is_superhost','instant_bookable','is_location_exact','require_guest_phone_verification','require_guest_profile_picture','requires_license','review_scores_accuracy','review_scores_checkin','review_scores_cleanliness','review_scores_communication','review_scores_location','review_scores_value')
completeData <- completeData %>%
  mutate_at(colsToFactor, ~factor(.))


#completeData$high_booking_rate<-as.factor(completeData$high_booking_rate)
colnames(completeData)

colsToFactor<-c(43:245)
completeData <- completeData %>%
  mutate_at(colsToFactor, ~factor(.))
#completeData<-completeData[,-96]



gc()



#completeData$high_booking_rate<-as.factor(completeData$high_booking_rate)
#levels(completeData$high_booking_rate) <- c("No", "Yes")


gc()

#completeData<-completeData %>% filter(market=='New York')

set.seed(1234)

library(data.table)

library(Matrix)



myvars <- c("high_booking_rate", "host_is_superhost","amenities_.Self.check.in.","host_response_time",
            "amenities_.Hot.water.","amenities_.Free.street.parking.","amenities_.Dishes.and.silverware.","amenities_Refrigerator","amenities_.Coffee.maker.","host_listings_count","amenities_Microwave","cancellation_policy","availability_90","availability_60","availability_30","availability_365","amenities_.Extra.pillows.and.blankets.","longitude","amenities_.Cooking.basics.","amenities_.Luggage.dropoff.allowed.","latitude","amenities_.Bed.linens.","amenities_.Hair.dryer.","amenities_Keypad","minimum_nights","extra_people","cleaning_fee","amenities_.Family.kid.friendly.","guests_included","price","property_type","amenities_Shampoo","amenities_Stove","amenities_Iron","amenities_.translation.missing..en.hosting_amenity_50.","review_scores_value","amenities_.Long.term.stays.allowed.","price_score","amenities_.24.hour.check.in.","host_response_rate","amenities_Hangers","amenities_.Garden.or.backyard.","amenities_Oven","amenities_.Fire.extinguisher.","amenities_Gym","amenities_.Laptop.friendly.workspace.","amenities_Elevator","maximum_nights","amenities_.Patio.or.balcony.","review_scores_accuracy","review_scores_checkin","amenities_Lockbox","host_verifications","amenities_.First.aid.kit.","amenities_.Carbon.monoxide.detector.","security_deposit","amenities_Internet","review_scores_communication","amenities_.Single.level.home.","amenities_Pool","amenities_Essentials","amenities_.Pets.live.on.this.property.","amenities_.Bedroom.comforts.","amenities_.Bathroom.essentials.","amenities_.Toilet.paper.","amenities_.Well.lit.path.to.entrance.","amenities_Dog.s.","amenities_.Bath.towel.","amenities_.Smoke.detector.","bathrooms","accommodates","review_scores_location","amenities_Wifi","review_scores_value","review_scores_cleanliness","host_identity_verified","is_location_exact","requires_license","require_guest_profile_picture","amenities","host_sinceD","amenities_.Pack..n.Play.travel.crib.","amenities_.No.stairs.or.steps.to.enter.","amenities_.Body.soap.","amenities_.Room.darkening.shades.","amenities_.Safety.card.","amenities_Bathtub","amenities_.Children.s.books.and.toys.","amenities_Heating","amenities_.Hot.tub.","amenities_.Wide.entrance.for.guests.","amenities_Dishwasher","amenities_.Extra.space.around.bed.","amenities_Cat.s.","amenities_Netflix","amenities_.Cable.TV.","amenities_.Luggage.dropoff.allowed.","amenities_.Smart.TV.","market","amenities_Internet","bedrooms","amenities_Printer","amenities_.Disabled.parking.spot.","amenities_.Mini.fridge.","amenities_.Gas.oven.","amenities_.24.hour.check.in.","amenities_.Full.kitchen.","amenities_Washer","amenities_Other","instant_bookable","amenities_.Formal.dining.area.","room_type","review_scores_ratingOG")

completeData <- completeData[myvars]

library(dummies)

completeData2 <- dummy.data.frame(completeData[-2], sep = ".")

levels(completeData$host_is_superhost) <- c(0,1,2)
target<-completeData$host_is_superhost


trainMatrix <- data.matrix(completeData2[-1])
#testMatrix <- data.matrix(dffTest[-1])
trainMatrix<-scale(trainMatrix)
#testMatrix<-scale(testMatrix)

#dim(dffTrain)

param <- list("objective" = "multi:softprob",scoring='auc',"num_class"=4)


nround = 195            #this number is the number of trees when test mlogloss is minimum during cross-validation
bst = xgboost(data = trainMatrix, label = target, param=param, nrounds = nround)

#predict the model

#ypred = predict(bst, testMatrix)

#pred <-  as.numeric(ypred > 0.5)
#CM_Validation <- confusionMatrix(as.factor(pred),as.factor(dffTest$high_booking_rate))
#CM_Validation


importance <- xgb.importance(feature_names = colnames(completeData2[-1]), model = bst)
importance
```

```{r}
##This is a table of all the features in the data and their importance gain towards deciding host status from the model of XGboost.
importance
```




```{r,echo=FALSE}
library(ggplot2)
importance2 <- within(importance, Feature[Gain<0.025] <- 'Other')
importance2<-importance2 %>% 
  mutate(importance=Gain/sum(Gain)*100)
summed<-sum(importance2[11:132,5])
library(tidyverse)
importance2<-importance2 %>% add_row(Feature = "Other", importance = summed)
importance2<-importance2[c(1:10,133),]


# Barplot
bp<- ggplot(importance2, aes(x="", y=importance, fill=Feature))+
geom_bar(width = 1, stat = "identity")
#bp

pie <- bp + coord_polar("y", start=0)
#pie



blank_theme <- theme_minimal()+
  theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.border = element_blank(),
  panel.grid=element_blank(),
  axis.ticks = element_blank(),
  plot.title=element_text(size=14, face="bold")
  )
library(scales)
pie + geom_text(aes(label = paste0(round(importance2$importance))), position = position_stack(vjust = 0.5))

```



```{r,echo=FALSE}

completeData3 <- dummy.data.frame(completeData, sep = ".")

#levels(completeData$host_is_superhost) <- c(0,1,2)
target<-completeData$high_booking_rate


trainMatrix <- data.matrix(completeData3[-1])
#testMatrix <- data.matrix(dffTest[-1])
trainMatrix<-scale(trainMatrix)
#testMatrix<-scale(testMatrix)

#dim(dffTrain)

param <- list("objective" = "binary:logistic",scoring='auc')


nround = 195            #this number is the number of trees when test mlogloss is minimum during cross-validation
bst = xgboost(data = trainMatrix, label = target, param=param, nrounds = nround)

#predict the model

#ypred = predict(bst, testMatrix)

#pred <-  as.numeric(ypred > 0.5)
#CM_Validation <- confusionMatrix(as.factor(pred),as.factor(dffTest$high_booking_rate))
#CM_Validation


importance <- xgb.importance(feature_names = colnames(completeData3[-1]), model = bst)
importance<-importance %>% filter(str_detect(Feature, "amenities_"))


importance2 <- within(importance, Feature[Gain<0.0035] <- 'Other')
importance2<-importance2 %>% 
  mutate(importance=Gain/sum(Gain)*100)
importance2<-importance2[-2,]
summed<-sum(importance2[8:55,5])
library(tidyverse)
importance2<-importance2 %>% add_row(Feature = "Other", importance = summed)
importance2<-importance2[c(1:7,56),]


# Barplot
bp<- ggplot(importance2, aes(x="", y=importance, fill=Feature))+
geom_bar(width = 1, stat = "identity")




```
```{r}
bp

```
 
 


